XRONOS: an open data infrastructure for archaeological chronology

### 2024-12-02 paper.qmd
Update TODO list

<!--
* [x] First draft
* [ ] Complete references:
  * [x] Introduction
  * [ ] State of the art
  * [ ] Concept
  * [ ] Implementation
  * [ ] Evaluation
  * [ ] Appendix table
* [ ] Figures and tables
  * [x] FIGURE: graph of number of datasets through time
  * [x] FIGURE: map of number of dates in datasets
  * [ ] FIGURE: distribution of radiocarbon dates in c14bazAAR / IntChron / p3k14c / XRONOS
  * [x] FIGURE: data model
  * [x] FIGURE: GUI screenshots (data browser, c14 show view, version history, data curation)
  * [ ] TABLE: list of 'issues'
  * [ ] APPENDIX: table of datasets
* [ ] Other TODOs
* [ ] Copyedit:
  * [ ] Introduction
  * [ ] State of the art
  * [ ] Concept
  * [ ] Implementation
  * [ ] Evaluation
  -->

@@

The XRONOS project was carried under the direction of Albert Hafner. 
Individual contributors to the XRONOS database to date include Chiara Huwiler, Rivana Moser, Tomasz Chmielewski, and Stephanie Döppler. 
A complete and up-to-date list of acknowledgements for the project can be found at <https://xronos.ch/about/acknowledgements>.

>>>>

<!--
* [x] First draft
* [x] References
* [x] Figures and tables
* [ ] SM1 (data/c14_datasets.tsv)
  * [ ] References
  * [ ] Nice PDF version
* [ ] Other TODOs
* [ ] Copyedit:
  * [ ] Introduction
  * [ ] State of the art
  * [ ] Concept
  * [ ] Implementation
  * [ ] Evaluation
  -->

@@

The XRONOS project was carried under the direction of Albert Hafner. 
Individual contributors to the XRONOS database to date include Chiara Huwiler, Rivana Moser, Tomasz Chmielewski, and Stephanie Döppler. 
A complete and up-to-date list of acknowledgements for the project can be found at <https://xronos.ch/about/acknowledgements>.
<!-- TODO: peer reviewers -->
